Nested Sampling with Multiple Objective Functions

### 2018-06-13 doc/ms.tex
Include the new figures

\section{Example 1: Known solution}
In the software repository, this example is implemented in
{\tt examples/Demo.h} and {\tt examples/Demo.cpp}.
We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The first objective function is quadratic in form, such that the canonical
distributions are iid normal centered at $(0.5, 0.5, ..., 0.5)$:
\begin{eqnarray}
E_1(\xx) &=& \sum_{i=1}^{100} \left(\frac{x_i - 0.5}{0.1}\right)^2.
\end{eqnarray}
The second objective function, given by
\begin{eqnarray} 
E_2(\xx) &=& \sin^2(10 \pi x_i),
\end{eqnarray}
upweights states where coordinates $\{x_i\}$
are close to 0, 0.1, 0.2, ..., 0.9 and 1.
The canonical distributions for this system should draw the coordinates
towards 0.5 (due to $E_1$) and towards the troughs of $E_2$, with the
relative importance of these effects determined by the values of the
inverse temperatures $\beta_1$ and $\beta_2$.

The true partition function (computed numerically) and the Kullback-Leibler
divergence from the prior to the canonical distribution are shown in
Figure~\ref{fig:truth} as a function of two temperatures.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.75]{figures/demo_truth.pdf}
\caption{The true partition function and KL divergence (from the prior to
the canonical distribution) as a function of two temperatures for the
test problem.\label{fig:truth}}
\end{figure}

>>>>

\section{Example 1: Known solution}
In the software repository, this example is implemented in
{\tt examples/Demo.h} and {\tt examples/Demo.cpp}.
We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The first objective function is quadratic in form, such that the canonical
distributions are iid normal centered at $(0.5, 0.5, ..., 0.5)$:
\begin{eqnarray}
E_1(\xx) &=& \sum_{i=1}^{100} \left(\frac{x_i - 0.5}{0.1}\right)^2.
\end{eqnarray}
The second objective function, given by
\begin{eqnarray} 
E_2(\xx) &=& \sin^2(10 \pi x_i),
\end{eqnarray}
upweights states where coordinates $\{x_i\}$
are close to 0, 0.1, 0.2, ..., 0.9 and 1.
The canonical distributions for this system should draw the coordinates
towards 0.5 (due to $E_1$) and towards the troughs of $E_2$, with the
relative importance of these effects determined by the values of the
inverse temperatures $\beta_1$ and $\beta_2$. Three example canonical
distributions are shown in Figure~\ref{fig:demo_canonical}.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.75]{figures/demo_canonical.pdf}
\caption{Three canonical distributions for different values of the two
temperatures $T_1$ and $T_2$. These are for the one-dimensional case, but
in this example, the 100 dimensional canonical distributions are independent
and have these distributions as their marginals.\label{fig:demo_canonical}}
\end{figure}

The true partition function (computed numerically) and the Kullback-Leibler
divergence from the prior to the canonical distribution are shown in
Figure~\ref{fig:demo_truth} as a function of two temperatures.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.75]{figures/demo_truth.pdf}
\caption{The true partition function and KL divergence (from the prior to
the canonical distribution) as a function of two temperatures for the
test problem.\label{fig:demo_truth}}
\end{figure}
